oai
=======

```{r echo=FALSE}
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  collapse = TRUE,
  comment = "#>"
)
```

[![Build Status](https://travis-ci.org/sckott/oai.svg?branch=master)](https://travis-ci.org/sckott/oai)

`oai` is an R client to work with OAI-PMH services.

There is [an OAI-PMH client][harv] but it's built on `XML` and `RCurl`, packages basically replaced now by `xml2` and `httr`/`curl`, respectively. `oai` is built on `xml2` and `httr`. In addition, attempt to give 
back data.frame's whenever possible to make data comprehension, manipulation, and visualization easier. 

## Install

```{r eval=FALSE}
devtools::install_github("sckott/oai")
```

```{r}
library("oai")
```

## Identify

```{r}
id("http://oai.datacite.org/oai")
```

## ListRecords

```{r}
list_records(from = '2011-05-01T', until = '2011-08-15T')
```

## GetRecords

```{r}
get_records(c("oai:oai.datacite.org:32255", "oai:oai.datacite.org:32325"))
```

## Count Identifiers

```{r}
count_identifiers("http://oai.datacite.org/oai")
```

[harv]: http://cran.rstudio.com/web/packages/OAIHarvester/
