<!--
%\VignetteEngine{knitr::knitr}
%\VignetteIndexEntry{oai introduction}
%\VignetteEncoding{UTF-8}
-->

```{r echo=FALSE}
knitr::opts_chunk$set(
	comment = "#>",
	collapse = TRUE,
	warning = FALSE,
	message = FALSE
)
```

oai introduction
================

A general purpose client to work with any 'OAI-PMH' service. The 'OAI-PMH' protocol is described at [http://www.openarchives.org/OAI/openarchivesprotocol.html](http://www.openarchives.org/OAI/openarchivesprotocol.html). The main functions follow the OAI-PMH verbs:

* `GetRecord`
* `Identify`
* `ListIdentifiers`
* `ListMetadataFormats`
* `ListRecords`
* `ListSets`

## Get oai

Install from CRAN

```{r install, eval=FALSE}
install.packages("oai")
```

Or install the development version from GitHub

```{r installgh, eval=FALSE}
devtools::install_github("ropensci/oai")
```

Load `oai`

```{r load}
library("oai")
```

## Identify

```{r}
id("http://oai.datacite.org/oai")
```

## ListIdentifiers

```{r}
list_identifiers(from = '2011-05-01T', until = '2011-09-01T')
```

## Count Identifiers

```{r}
count_identifiers()
```

## ListRecords

```{r}
list_records(from = '2011-05-01T', until = '2011-08-15T')
```

## GetRecords

```{r}
get_records(c("oai:oai.datacite.org:32255", "oai:oai.datacite.org:32325"))
```

## List MetadataFormats

```{r}
list_metadataformats(id = "oai:oai.datacite.org:32348")
```

## List Sets

```{r}
list_sets("http://oai.datacite.org/oai")
```

## Examples of other OAI providers

### Global Biodiversity Information Facility

Identify

```{r}
id("http://api.gbif.org/v1/oai-pmh/registry")
```

Get records

```{r}
get_records(c("816f4734-6b49-41ab-8a1d-1b21e6b5486d", "95e3042f-f48d-4a04-8251-f755bebeced6"),
            url = "http://api.gbif.org/v1/oai-pmh/registry")
```

### Biodiversity Heritage Library

Identify

```{r}
id("http://www.biodiversitylibrary.org/oai")
```

Get records

```{r}
get_records(c("oai:biodiversitylibrary.org:item/7", "oai:biodiversitylibrary.org:item/9"),
            url = "http://www.biodiversitylibrary.org/oai")
```
