<!--
%\VignetteEngine{knitr::knitr}
%\VignetteIndexEntry{oai introduction}
%\VignetteEncoding{UTF-8}
-->

```{r echo=FALSE}
knitr::opts_chunk$set(
	comment = "#>",
	collapse = TRUE,
	warning = FALSE,
	message = FALSE
)
```

oai introduction
================

A general purpose client to work with any 'OAI-PMH' service. The 'OAI-PMH' protocol is described at [http://www.openarchives.org/OAI/openarchivesprotocol.html](http://www.openarchives.org/OAI/openarchivesprotocol.html). The main functions follow the OAI-PMH verbs: 

* `GetRecord`
* `Identify`
* `ListIdentifiers`
* `ListMetadataFormats`
* `ListRecords`
* `ListSets`

## Get oai

Install from CRAN (when it lands)

```{r install, eval=FALSE}
install.packages("oai")
```

Or install the development version from GitHub

```{r installgh, eval=FALSE}
devtools::install_github("sckott/oai")
```

Load `oai`

```{r load}
library("oai")
```

## Identify

```{r}
id("http://oai.datacite.org/oai")
```

## ListIdentifiers

```{r}
list_identifiers(from = '2011-05-01T', until = '2011-09-01T')
```

## Count Identifiers

```{r}
count_identifiers()
```

## ListRecords

```{r}
list_records(from = '2011-05-01T', until = '2011-08-15T')
```

## GetRecords

```{r}
get_records(c("oai:oai.datacite.org:32255", "oai:oai.datacite.org:32325"))
```

## List MetadataFormats

```{r}
list_metadataformats(id = "oai:oai.datacite.org:32348")
```

## List Sets

```{r}
list_sets("http://oai.datacite.org/oai")
```
